---
title: "package_name-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_name-vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eaziReda)
```

# Introduction to eaziReda

Exploratory data analysis (EDA) and data preprocessing are two crucial
steps in the data analysis workflow. To be specific, the users usually
need to do the following tasks:

-   checking missing values - detecting outliers

-   plotting correlation plots between features

-   plotting histograms/bar plots for each individual features

-   imputation

-   dealing with outliers

The eaziReda that wraps all of those tasks into several convenient
functions that allow the users to quickly and easily carry out EDA along
with some simple preprocessing:

-   It can report the number/percentage of missing values for all
    columns in a given dataframe as well as giving the user an option of
    imputing the missing values all together based on the imputation
    methods the user specifies.

-   It can identify all outliers for a given column/vector based on the
    methods the user specifies as well as giving the user an option of
    removing the outliers all together.

-   It can automatically generate a correlation plot based on user's
    choice of features.

-   It can automatically generate histograms and bar plots based on
    user's choice of features.

# Data: mtcars

To illustrate how different functions of the `eaziReda` package work, we
will use the `mtcars` dataset, which is included in the base R datasets.
Also, in order to show the full picture of functions, we choose to
modify the `mtcars` dataset and create a new dataset called `mtcars_new`
by making the data more complicated and unclean. The modifications are
shown as below:

### Change the types of two columns to categorical:

```{r creat_cat}
mtcars_new <- mtcars %>% 
  dplyr::mutate(cyl = as.factor(cyl), gear = as.factor(gear))
```

### Create some missing values:

```{r creat_missing}
  mtcars_new$mpg[2:5] <- NA
  mtcars_new$cyl[2:5] <- NA
```

### Create some outliers:

```{r creat_outliers}
mtcars_new$hp[2:5] <- 500
```

After simple modification, the first 10 rows of `mtcars_new` are shown
as follows:

```{r show}
head(mtcars_new, 10)
```

# Identifying Missing Values with `missing_detect()`

`missing_detect()` can be used to detect the missing values of a given
dataset. There is only one argument for this function, which can be
either base-R dataframe or tibble. The output is a table that listing
the number of missing values (`n_missing`) and the percentage of missing
values for each column (`percent`).

For example, we can assess the missing values in the `mtcars_new`.

```{r missing_detect}

missing_detect(mtcars_new)
```

# Imputing Missing Values with `missing_impute()`

`missing_detect()` can be used to impute the missing values all together
for a given dataset. The first argument is the dataset, which can be
either base-R dataframe or tibble. The second argument is the method
used for imputing numerical missing values (one of "mean", "median",
"drop"). The third argument is the method used for imputing
non-numerical missing values (one of "most\_frequent", "drop"). The
output is a imputed version of the input dataset.

For example, we can impute the `mtcars_new` by filling the NAs by column
mean if NA appears in numerical column, and filling the NAs by most
frequent values otherwise. The table below shows the first 10 rows of
the imputed `mtcars_new`.

```{r missing_impute}
mtcars_new_imputed <- missing_impute(mtcars_new, method_num = "mean", method_non_num = "most_frequent")
head(mtcars_new_imputed, 10)
```

# Detecting the Outliers with `outliers_detect()`

`outlier_detect()` can be used to detect the outliers for a given
vector/column. The first argument is the vector that the user would like
to detect outliers for. The second argument is method to detect
outliers.(one of "zscore", "iqr", "iforest"). The output is a boolean
vector with indices marked TRUE for the outliers.

For example, we can assess the outliers for the column `hp` based on the
rule of interquartile range (IQR).

```{r outlier_detect}
outliers_detect(mtcars_new$hp, method = "iqr")
```

# Removing the Outliers with `remove_outliers()`

`remove_outliers()` can be used to remove the outliers for a given
vector/column. The first argument is the vector that the user would like
to delete the outliers for. The second argument is a boolean vector with
outliers marked true. The user can directly pass the results of
outliers\_detect() as the second argument and remove the corresponding
outliers easily. The output is a vector with outliers deleted from the
input vector.

For example, we can remove the outliers that we identified before for
the column `hp`.

```{r outlier_remove}
remove_outliers(mtcars_new$hp, outliers_detect(mtcars_new$hp, method = "iqr"))
```

# Plotting Different Features with `histograms()`

`histograms` can be used to create plots given a list of different kinds
of features (columns). The first argument is the dataset, which can be
either base-R dataframe or tibble. The second argument is a character
vector that contains all the column names that the user would like to
plot for. The third argument is an integer that indicates the number of
columns in faceted chart produced. The output is a faceted chart that
includes one plot each column the user specifies in the second argument.
For numerical columns, the corresponding output plots will be the
histograms. For categorical columns, the corresponding output plot will
be the bar charts.

For example, we can plot and explore the columns: `mpg`, `disp`, `cyl`,
and `gear` together.

```{r hist, fig.width=8, fig.height=8}
histograms(mtcars_new, features=c("mpg", "disp", "cyl", "gear"), num_cols = 2)
```

# Plotting Correlations with `corr_plot()`

`corr_plot()` can be used to create a pairwise correlation plot given a
list of numerical features (columns). The first argument is the dataset,
which can be either base-R dataframe or tibble. The second argument is a
character vector that contains all the names of the numerical columns
that the user would like to plot for. The third argument is the method
to calculate the correlation (one of "pearson", "spearman" or
"kendall"). The output is a correlation matrix (heatmap) showing the
correlation between the specified columns.

For example, we can explore the pearson correlation coefficients between
the columns: `mpg`, `disp`, and `hp`.

```{r corr, fig.width=7, fig.height=7}
corr_plot(mtcars_new, features=c("mpg", "disp","hp"), method = 'pearson')
```

# Key Advantages

-   This package is implemented with the functions to do both EDA and
    data proprocessing.After EDA, the user might not need to explore
    other packages to do such proprocessing tasks.
-   The plotting functions can take the argument as list of features. So
    the user do not need to run the same plotting function over and over
    again. The plots are well-organized already.
-   Lots of flexibility and customization available.
